\documentclass{./BeekeepingBook}

\title{\Huge 324 Beekeeping\\ \vspace{1 ex} \Large Integrated Apiary Management for Small Scale Beekeeping}

\author{Joe Collins}
\date{\DTMnow}

\begin{document}
 
\maketitle
\tableofcontents

\chapter{Overview}

\section*{Keeping Bees}

Small scale or hobbie beekeepers tend to have a range of desires:

\begin{itemize}
  \item to make enough honey for friends and family.
  \item to keep healthy bees
  \item to 
\end{itemize}

Beginners ask:

\begin{itemize}
  \item How long do the bees live?
  \item How much honey do you get?
  \item How much work is it?
  \item How many hives do you have?
\end{itemize}

Bee keepers want to:

\begin{itemize}
  \item Maximize the chance of their bees surviving
  \item Maximize honey production
  \item Minimize the amount of work
  \item Minimize the amount of equipment
\end{itemize}

\subsection*{Recommendations}

\begin{description}
  \item[Relic acid place some frames each year]
  \item[Treat with oxalic mid winter]
  \item[Begin ApiGuard before the middle of August]
  \item[Always have second colony to fix the first]
  \item[Always have a hive spare]
\end{description}

\subsection*{Response}

Doctrine of planned action.

Minimal equipment

\chapter{Preparation: Avoid Starvation and Queen Selection}
\include{03March}
\include{04April}

\chapter{Production: Queens and Honey}
\include{05May}
\include{06June}
\include{07July}
 
\chapter{Protection: Varroa and Feeding}
\include{08August}
\include{09September}
\include{10October}

\chapter{Preservation: Varroa and Hardware}
\include{11November}
\include{12December}
\include{01January}
\include{02February}

\appendix
\chapter{Appendix}
\section{Complete Apriary}
\begin{apiary}{Stuff}
    \path (0,7.5) pic{roof=feeder};
    \path (0,6)  pic{super=super};
    \path (0,4)  pic{brood=8F};
    \path (0,2)  pic{brood=8F};
    \path (0,0)  pic{stand};
    
    \path (4,7.5) pic{roof=candy};
    \path (4,6)  pic{super=super};
    \path (4,4)  pic{brood=8F};
    \path (4,2)  pic{brood=8F};
    \path (4,0)  pic{stand};

    \path (8,7.5) pic{roof=candy};
    \path (8,6) pic{super=super};
    \path (8,4) pic{brood=8F};
    \path (8,2) pic{brood=8F};
    \path (8,0) pic{stand};

    \path (12,7.5) pic{roof=candy};
    \path (12,6) pic{super=super};
    \path (12,4) pic{brood=8F};
    \path (12,2) pic{brood=8F};
    \path (12,0) pic{stand};

    \path (16,7.5) pic{roof=candy};
    \path (16,6) pic{super=super};
    \path (16,4) pic{brood=8F};
    \path (16,2) pic{brood=8F};
    \path (16,0) pic{stand};

    \path (20,7.5) pic{roof=candy};
    \path (20,6) pic{super=super};
    \path (20,4) pic{brood=8F};
    \path (20,2) pic{brood=8F};
    \path (20,0) pic{stand};
    
    \path (24,7.5) pic{roof=candy};
    \path (24,6) pic{super=super};
    \path (24,4) pic{brood=8F};
    \path (24,2) pic{brood=8F};
    \path (24,0) pic{stand};
\end{apiary}

\section{Inventory Hive of Equipment}

\begin{description}
  \item[8 Stands] 6 for hives in the season, one to swap and one under the supers in the airing cupboard.
  \item[7 Brood Boxes] 6 out being used with and one spare to swap for repairs.
  \item[6 Floors] all out a the peak of the season.
  \item[3 Queen Excluders] 2 on the production hives and 1 under the swarm you just caught.
\end{description}

\section{Inventory of Beekeeper Equipment}

\begin{description}
  \item[Suit]  
  \item[Rubber Gloves] 
  \item[Wellingtons] 
  \item[Smoker] 
  \item[Hive Tool] 
  \item[Marking Pen] yellow, because it is easiest to spot.
  \item[Crown of Thorns]  to capture the queen.
  \item[Jar of Pins]  to mark frames that have queen cells on or have been put in hives to test for queenlessness.
  \item[Cocktail Sticks]  to extract lavae for examination.
  \item[2 hive covers] to cover the first brood when you are looking in the second.
  \item[2 Cargo Straps] to help with moving hives. 
  \item[Sheets of Newspaper] to wrap culled drone comb in.
\end{description}

\section{Annual of Consumeables}

\begin{description}
  \item[22 Brood Frames] because you will sell two complete colonies
  \item[22 Sheets of Wired Brood Wax] for above 
  \item[22 Red End Spacers] for the North and West ends of above.
  \item[22 Green End Spacers] for the South and East ends of above.
  \item[Apiguard or MAQS for 3 hives] to treat at the end of the season
  \item[Oxalic acid for 3 hives] to treat in the middle of winter
  \item[30 kg Sugar] to feed at the end of the season
\end{description}

\end{document}
