% !TeX root = 00beekeeping.tex
\section{April: Reduce to Two Colonies}

April is the beginning of the old farming (and tax) year.
Colonies that survived the winter should be building up.
Now is the time to ensure that the year begins with only two colonies.
Two is the minimum number of colonies to keep since
a lost queen in one colony can be replaced using eggs from the other colony.
The intention is to get down to two strong colonies on 18 frames each (9Fx9F).

\subsection{First Inspection}

\begin{description}
  \item[Confirm queen present and laying] looking for eggs and larvae.
  \item[All three are strong] Select for sale based on temperament, size or the state of the frames.
  \item[One Colony is weak]
  \item[Two Colonies are weak]
  \item[One Colony is dead] 
\end{description}

\subsection*{Select for Removal}

\begin{apiary}{Select of removal}
    \path (4,6) pic{roof=feeder};
    \path (4,4) pic{brood=8F};
    \path (4,2) pic{brood=8F};
    \path (4,0) pic{stand};

    \node at (13.5,8) {Selected for Removal};
    \path (12,6) pic{roof=feeder};
    \path (12,4) pic{brood=8F};
    \path (12,2) pic{brood=8F};
    \path (12,0) pic{stand};

    \path (20,6) pic{roof=feeder};
    \path (20,4) pic{brood=8F};
    \path (20,2) pic{brood=8F};
    \path (20,0) pic{stand};
\end{apiary}


\subsection*{Prepare for Removal}

Shuffle for sale or give away.


\begin{apiary}{Stuff}
    \path (6,6) pic{roof};
    \path (6,4) pic{brood=9F};
    \path (6,2) pic{brood=9F};
    \path (6,0) pic{stand};

    \node at (13.5,6) {Remove or Sell};
    \path (12,4) pic{roof};
    \path (12,2) pic{brood=11F};
    \path (12,0) pic{stand};

    \path (18,6) pic{roof};
    \path (18,4) pic{brood=9F};
    \path (18,2) pic{brood=9F};
    \path (18,0) pic{stand};
\end{apiary}


\begin{description}
  \item[Open the hive for removal]
The colony selected for sale has 16 frames (8F x 8F).
Select 11 of the frames for sale.
And put in one box.
Shake off the other 5 frames and put 4 them in the other two colonies so the are now 18 frames (9F x 9F) each.
Stash or trash the 5 th frame.
\end{description}