\documentclass{./BeekeepingBook}

\title{Apiary Management Procedure}
\author{Joe Collins}
\setcounter{tocdepth}{3}

\begin{document}
\maketitle

\begin{abstract}

  Goals:

  \begin{itemize}
    \item Replace queens.
    \item Harvest some honey. 
    \item Renew some frames.
    \item Treat for varroa in summer and winter.
    \item Never have less than two colonies.
  \end{itemize}

  Approach sequence:

  \begin{enumerate}
    \item Start the season with two colonies.
    \item Raise two queens from those colonies so you have four colonies.
    \item Due to swarming so you might get another couple of colonies giving you six.
    \item At the end of the season reduce to three colonies by selling or uniting.
    \item Go into winter with three colonies.
    \item If all three survive the winter, sell one to start the season with two colonies. 
  \end{enumerate}

\end{abstract}

\clearpage
\tableofcontents

\clearpage
\section{Spring: Feeding and Queen Selection}
\begin{description}
  \item[February] Ensure there is enough equipment for 6 colonies.
  \item[March] Early feeding to avoid starvation.
  \item[April] Reduce to two colonies.
\end{description}
\input{02February}
\input{03March}
\input{04April}

\clearpage
\section{Summer: Production of Queens and Honey}
\begin{description}
  \item[May] Split the colonies to raise two new queens and early honey production.
  \item[June] Confirm the two new queens and collect swarms.
  \item[July] Swarm management and late honey production.
\end{description}
\input{05May}
\input{06June}
\input{07July}

\clearpage
\section{Autumn: Feeding for Winter}
\input{08August}
\input{09September}
\input{10October}

\clearpage
\section{Winter: Hive Maintenance}
\input{11November}
\input{12December}
\input{01January}

\clearpage
\section{Notes}
\subsection{Complete Apiary}
\begin{apiary}{Stuff}
    \path (0,7.5) pic{roof=feeder};
    \path (0,6)  pic{super=super};
    \path (0,4)  pic{brood=8F};
    \path (0,2)  pic{brood=8F};
    \path (0,0)  pic{stand};
    
    \path (4,7.5) pic{roof=candy};
    \path (4,6)  pic{super=super};
    \path (4,4)  pic{brood=8F};
    \path (4,2)  pic{brood=8F};
    \path (4,0)  pic{stand};

    \path (8,7.5) pic{roof=candy};
    \path (8,6) pic{super=super};
    \path (8,4) pic{brood=8F};
    \path (8,2) pic{brood=8F};
    \path (8,0) pic{stand};

    \path (12,7.5) pic{roof=candy};
    \path (12,6) pic{super=super};
    \path (12,4) pic{brood=8F};
    \path (12,2) pic{brood=8F};
    \path (12,0) pic{stand};

    \path (16,7.5) pic{roof=candy};
    \path (16,6) pic{super=super};
    \path (16,4) pic{brood=8F};
    \path (16,2) pic{brood=8F};
    \path (16,0) pic{stand};

    \path (20,7.5) pic{roof=candy};
    \path (20,6) pic{super=super};
    \path (20,4) pic{brood=8F};
    \path (20,2) pic{brood=8F};
    \path (20,0) pic{stand};
    
    \path (24,7.5) pic{roof=candy};
    \path (24,6) pic{super=super};
    \path (24,4) pic{brood=8F};
    \path (24,2) pic{brood=8F};
    \path (24,0) pic{stand};
\end{apiary}

\subsection{Inventory Hive of Equipment}

\begin{description}
  \item[8 Stands] 6 for hives in the season, one to swap and one under the supers in the airing cupboard.
  \item[7 Brood Boxes] 6 out being used with and one spare to swap for repairs.
  \item[6 Floors] all out a the peak of the season.
  \item[4 Queen Excluders] 2 on the production hives and 2 when the old colonies expand.
\end{description}

\subsection{Inventory of Beekeeper Equipment}

\begin{description}
  \item[Suit]  
  \item[Rubber Gloves] 
  \item[Wellingtons] 
  \item[Smoker] 
  \item[Hive Tool] 
  \item[Marking Pen] yellow, because it is easiest to spot.
  \item[Crown of Thorns]  to capture the queen.
  \item[Jar of Pins] to mark frames that have queen cells on (so you are careful with knocking them).
  \item[Cocktail Sticks]  to extract larvae for examination.
  \item[2 hive covers] to cover the first brood when you are looking in the second.
  \item[2 Cargo Straps] to help with moving hives. 
  \item[Sheets of Newspaper] to wrap culled drone comb in.
\end{description}

\subsection{Annual of Consumables}

\begin{description}
  \item[22 Brood Frames] because you will sell two complete colonies
  \item[22 Sheets of Wired Brood Wax] for above 
  \item[22 Red End Spacers] for the North and West ends of above.
  \item[22 Green End Spacers] for the South and East ends of above.
  \item[Apiguard or MAQS for 3 hives] to treat at the end of the season
  \item[Oxalic acid for 3 hives] to treat in the middle of winter
  \item[45 kg Sugar] to feed at the end of the season
  \item[2.5 kg Sugar] for candy blocks
  \item[3 x 750 ml take away dishes] for candy blocks
\end{description}

\subsection{Queen Raising}

\newcounter{rowno}
\setcounter{rowno}{0}
\begin{table}[H]%
\begin{center}
\begin{tabular}{>{\stepcounter{rowno}\therowno}lllcc}
\multicolumn{1}{r}{\textbf{Day}}  & \textbf{Queen} & \textbf{Early Beekeeper} \\
 & \rdelim\}{3}{3mm}[\textsf{Egg}] & $\leftarrow$ 1. \textbf{Remove queen} \\
\\
 & \multirow{2}{*}{\quad $\leftarrow$ Hatching} & \\
 \cline{1-1}
 & \rdelim\}{5}{3mm}[\textsf{Larva}] &  \\
 \\  \\  \\
 & \multirow{2}{*}{\quad $\leftarrow$ Sealing} & $\leftarrow$ 2. \textbf{Cull queen cells}  \\
\cline{1-1}
 & \rdelim\}{8}{3mm}[\textsf{Pupa}] &  \\
 \\  \\  \\  \\  \\ \\
 & \multirow{2}{*}{\quad $\leftarrow$ Emerging} \\
\cline{1-1}
 & \rdelim\}{5}{3mm}[\textsf{Maturing}] \\
\\  \\  \\  \\
\cline{1-1}
 & \rdelim\}{4}{3mm}[\textsf{Mating (typical)}] \\
\\  \\  \\
\cline{1-1}
 & \rdelim\}{2}{3mm}[\textsf{Sperm Transfer}] \\
 \\
\cline{1-1}
 & \rdelim\}{17}{3mm}[\textsf{Laying (typical)}] \\
\\ \\  \\  \\  \\  \\  \\  \\  \\  \\  \\  \\  \\  \\ 
 & & \multicolumn{2}{l}{$\leftarrow$  3. \textbf{Check}} \\
\end{tabular}
\caption{Swarm Control and Queen Raising}%
\end{center}
\end{table}

\end{document}
